---
title: "A4"
author: Anthony Edward Monreal Kemp
date: 10/18/2023
output: github_document
---

1.

A. Objective
B. Subjective
C. Objective
D. Subjective
E. Objective


2.

A.Empirical
B.Classical
C.Empirical

3.

A. Simple 
B. Simple
C. Compound
D. Simple
E. Compound

4.

A. Independent 
B. Mutually exclusive
C. Independent
D. Mutually exclusive
E. Collectively exhaustive


5. 

A. True
B. False
C. True

6.

It will be from 0-1


7. 

Pr (D) is the difference of the sum of Pr(A)+Pr(B)+Pr(C)

```{r}
A<- 0.23
D<- 1-(0.23+0.15+0.46)
D+A
```


8. 

The answer would be zero since they are all mutually exclusive.

9.
```{r}
Pr_A <- .13
Pr_B <- .36


0.13*0.36
```

10. 

0.5=0.3+x-0.3x
x=2/7


11.

0.7=0.4+x-0.4x
x=1/2

12.

0.6=0.4+x-0.4x
x=1/3

13.

A. factorial 12/7=
B. 1/6
C. 12!/5!*7!=792
D. 7!/2!*5!=21
E. 12*11=132
F. 7*6=42

14.

6c2 * 5c2 * 4c1 = 600

15.
6!= 720

16.

A. 15c6 = 5005
B. 10c3 * 5c3 = 120 * 10 = 1200
C. 10c4 * 5c2 = 210 *10 = 2100

17.
(1/52)*(3/52)^3 * 4c1 = 36/52^5

18.
(3/52)^3*(1/52)^2* 5c2
=90/ 52^5


19.
7: 3/18= 1/6
3:1/18

20.
0.8*0.5/0.8:0.5+0.3*0.5+0.1*0.5
=0.4/0.6
=2/3



From 21 to 26 I did not fonish, I fell ill over the weekend.
