---
title: "B2 Homework"
author: Anthony Edward Monreal Kemp
date: September 30, 2023
output: github_document
---

```{r}
library(tidyverse)
library(readr)
setwd("C:/Users/edwar/OneDrive/Documents/GitHub/poli210-course-materials/Homeworks/B2")
```

```{r}
CCAP <- read_csv("CCAP.csv")
View(CCAP)
head(CCAP, n=4)
```

```{r}
gay <- read_csv("gay.csv")
View(gay)
head(gay, n=4)
```

```{r}
grades <- read_csv("grades.csv")
View(grades)
```

```{r}
dim(gay)
```
```{r}
dim(CCAP)
```

1. The distributions look similar on the X-axis, however the frequency, is doubled in the first histogram compared to the second histogram. This could cause a problem 
since this is counting a number of times an event had occurred.
```{r}

hist(CCAP$feel)

```

```{r}
hist(gay$feel1)

```
```{r}
hist(CCAP$feel, breaks = 10,
     main = "Voter's Feeling Towards Gay Men/Women")


```

```{r}
hist(gay$feel1, breaks = 10,
     main = "Feelings Towards Gay Men/Women Before Canvassers Field") 
```



2.

```{r}
summary(CCAP$feel)
```

```{r}
sd(CCAP$feel)
```

```{r}
summary(gay$feel1)
```
```{r}
sd(gay$feel1)
```
Yes, the two distributions have similar descriptive statistics.


3.Yes, because a sample of nation US voters should follow the same descriptive statistics since central limit theorem states that large samples from a population will be normally distributed.


4.
a.

```{r}
control_group <- gay[gay$treatment=="No Contact",]
```
```{r}
ggplot(data = control_group) +
      geom_point(mapping = aes(x = feel1, y= feel2))

```
b.
```{r}
ggplot(data = control_group) +
      geom_point(mapping = aes(x = feel1, y= feel3))
```
c.
```{r}
ggplot(data = control_group) +
      geom_point(mapping = aes(x = feel1, y= feel4))
```

Yes it looks like the respondents in the gay marriage experiment have relatively stable feelings overtime.


5.
```{r}
cor(gay$feel1, gay$feel2, use = "complete.obs")

```

```{r}
cor(control_group$feel1, control_group$feel3, use = "complete.obs")
```
```{r}
cor(control_group$feel1, control_group$feel4, use = "complete.obs")
```

6. Yes I think the data is fabricated.



Predicting Course Grades Using Midterm Scores

```{r}
grades<-read.csv("grades.csv")
view(grades)

head(grades)

```
1. 
a. Each observation is representing a student and their scores on their midterm, final, and overall class grade. gradeA variable is a yes or no binary variable if the student received an A in that class. 

b. X variables are the midterm and final variables
c. y variable is the final grade of the class

d. 
```{r}
cor(grades$midterm, grades$final, use = "complete.obs")

```
Yes it is looks like the relationship is strongly linear.


2.
a. & c.
```{r}
plot(x=grades$midterm, y=grades$final)
fit<-lm(final~midterm, data = grades)
abline(fit)
```
```{r}
lm(final~midterm, data = grades)
```
b. final= -6.0059+0.9704*midterm
Y is 'overall' class grade variable
X is 'midterm' meaning each students midterm score
alpha: value of Y if X is zero
beta: increase in Y associated with one unit increase in X

3. 
```{r}
#a
-6.0059+0.9704*80

#b 
-6.0059+0.9704*90

#c
0.9704*10



```
4. 
```{r}
cor(x= grades$midterm, y=grades$final)^2
```

I would interpret that this as the variables being displayed are showing 51% of the data is being explained by the independent variable being held with the dependent variable.









