---
title: "B3 Homework"
author: "Anthony Kemp"
date: "2023-10-17"
output: html_document
---
```{r}
install.packages("e1071")
library(tidyverse)
library(e1071)
```
Chp. 1

Problem #22
6 children in total
3 boys
3 girls
All births are equally likely to happen

I used the factorial combination section from the other book to solve this.

(3!)(3!)/6! = 0.05

Problem #34
```{r}
sims <- 100000
dice <- c(1,2,3,4,5,6)

roll_count <- 0
fav_outcome <- 0


for (i in 1:sims) {
      roll <- sample(x=dice, size=30, replace=TRUE)
      for(v in 1:6){
      a <- sum(roll==v)
      if(a==5){
        roll_count <- roll_count + 1
      }
      } 
      if(roll_count==6){
        fav_outcome <- fav_outcome + 1 
      }
      roll_count <-0
     }

answer <- fav_outcome/sims
answer

```

Chp. 2

Problem #2
```{r}
twin_type <- c("fraternal","fraternal","identical")
frat_combo <- c("BB","BG","GB","GG")
ident_combo <- c("BB","GG")

ident_BBcount <- 0
BB_count <- 0

for (i in 1:sims){
  twin_typei <- sample(twin_type, 1)
  if(twin_typei=="fraternal"){
    sex_combo <- sample(frat_combo, 1)
  }
  else{
    sex_combo <- sample(ident_combo, 1)
  }
  if(twin_typei=="identical" & sex_combo == "BB"){
    ident_BBcount <- ident_BBcount + 1
  }
  if(sex_combo == "BB"){
    BB_count <- BB_count+1
  }
}

answer <- ident_BBcount/BB_count
answer

```

Problem #32


For all scenarios the probability is 2/3 = 66,6%.

If A\>B is independent of B\>C and should have the same probability no matter the condition.

The event B\>C is not independent of C\>D and the probability should be lower for B\>C given that C\>D.


```{r}
a <- c(4,4,4,4,0,0)
b <- c(3,3,3,3,3,3)
c <- c(6,6,2,2,2,2)
d <- c(5,5,5,1,1,1)

a_count <- 0
b_count <- 0
c_count <- 0
d_count <- 0

aacount <- 0
abcount <- 0

for (i in 1:sims){
  a_roll <- sample(x=a, size=1, replace = TRUE)
  b_roll <- sample(x=b, size=1, replace = TRUE)
  c_roll <- sample(x=c, size=1, replace = TRUE)
  d_roll <- sample(x=d, size=1, replace = TRUE)
  
  # PART A
  if(a_roll>b_roll){
    a_count <- a_count + 1
  }
   if(b_roll>c_roll){
    b_count <- b_count + 1
   }
   if(c_roll>d_roll){
    c_count <- c_count + 1
   }
   if(d_roll>a_roll){
    d_count <- d_count + 1
   }
 
   # PART B
  if(b_roll>c_roll){
    if(a_roll>b_roll){
      aacount <- aacount + 1
      }
    }
  if(b_roll>c_roll){
    if(c_roll>d_roll){
      abcount <- abcount + 1
      }
    }
}

a_answer <- a_count/sims
b_answer <- b_count/sims
c_answer <- c_count/sims
d_answer <- d_count/sims
a_answer




b_answer
c_answer
d_answer

ba_answer <- a_count/b_count
ba_answer

bb_answer <- abcount/c_count
bb_answer



```


Problem #38

```{r}
sims <- 100000
doors <- c("goat", "goat", "goat", "goat", "car", "goat", "goat")
result.switch <- result.noswitch <- rep(NA, sims)

  for (i in 1:sims) {
  ## randomly choose the initial door
  initialdoor <- sample(1:7, size = 1)
  result.noswitch[i] <- doors[initialdoor]
  remain <- doors[-initialdoor] # remaining six doors after initial door is chosen
  ## Monty chooses three doors with a goat
  if (doors[initialdoor] == "car"){ # initial door holds the car
    monty <- sample(1:6, size=3)
  } else{ # 5 goats and one car left
    car_placement <- which(grepl("car", remain))
    tmp <- c(1,2,3,4,5,6)
    monty <- sample(tmp[tmp!=car_placement], 3)
  }
    remain_stp2 <- remain[-monty] 
    result.switch[i] <- sample(remain_stp2, 1)
  }

mean(result.noswitch == "car")

mean(result.switch =="car")
```
Seeing the mean comparison, it would be more viable to switch doors for the car.






