---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



R version 4.3.1 (2023-06-16 ucrt) -- "Beagle Scouts"
Copyright (C) 2023 The R Foundation for Statistical Computing
Platform: x86_64-w64-mingw32/x64 (64-bit)

R is free software and comes with ABSOLUTELY NO WARRANTY.
You are welcome to redistribute it under certain conditions.
Type 'license()' or 'licence()' for distribution details.

R is a collaborative project with many contributors.
Type 'contributors()' for more information and
'citation()' on how to cite R or R packages in publications.

Type 'demo()' for some demos, 'help()' for on-line help, or
'help.start()' for an HTML browser interface to help.
Type 'q()' to quit R.

[Workspace loaded from ~/R for Data Science Book/R for Data Science Chp4/.RData]

> knitr::opts_chunk$set(echo = TRUE)
> plot(pressure)
> install.packages("tidyverse")
WARNING: Rtools is required to build R packages but is not currently installed. Please download and install the appropriate version of Rtools before proceeding:

https://cran.rstudio.com/bin/windows/Rtools/
Installing package into ‘C:/Users/edwar/AppData/Local/R/win-library/4.3’
(as ‘lib’ is unspecified)
trying URL 'https://cran.rstudio.com/bin/windows/contrib/4.3/tidyverse_2.0.0.zip'
Content type 'application/zip' length 430806 bytes (420 KB)
downloaded 420 KB

package ‘tidyverse’ successfully unpacked and MD5 sums checked

The downloaded binary packages are in
	C:\Users\edwar\AppData\Local\Temp\RtmpeumoA6\downloaded_packages
> 

4.4 Exercises

#1
#The second code does not work because it is not spelled correctly. The "i" is different in the second run of code.
my_variable <- 10
my_varıable

#2
library(tidyverse)
ggplot(dota = mpg)+
  geom_point(mapping = aes(x = displ, y = hwy))
#corrected code, dota was misspelled and should've been the word data within the parantheses.
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)
#corrected code, the syntax specifically needed were two equal signs and filter was misspelled. 
filter(mpg, cyl == 8)

filter(diamond, carat > 3)

diamonds #this is a data set.

#corrected code, diamonds variable was misspelled 
filter(diamonds, carat > 3)

#3 
# Alt+Shift+K brings up a quick reference short-key guide
